Automated segmentation and description of the internal morphology of human permanent teeth by means of micro-CT

### 2021-02-22 manuscript.tex
Corrected issues found by Reviewer2:wq [ci skip]
This build is based on
https://github.com/habi/zmk-tooth-cohort-method-manuscript/commit/b07ffd6d4f153f209ba316c2199aaa3684329b61.

This commit was created by the following CI build and job:
https://github.com/habi/zmk-tooth-cohort-method-manuscript/commit/b07ffd6d4f153f209ba316c2199aaa3684329b61/checks
https://github.com/habi/zmk-tooth-cohort-method-manuscript/runs/589062910

A preprint of this manuscript is available on \emph{bioRxiv} at \url{https://doi.org/10.1101/2020.10.27.356998} and has been submitted to \href{https://bmcoralhealth.biomedcentral.com/}{\emph{BMC Oral Health}}.
This version of the manuscript \href{https://github.com/habi/zmk-tooth-cohort-method-manuscript/compare/f9b3333c625228f4f28211a34f381b9f87c430b0...07a0a8aed6642483a4a54a01d1578fe325802f88}{has been updated} since the preprint deposition.

This manuscript
(\href{https://habi.github.io/zmk-tooth-cohort-method-manuscript/v/07a0a8aed6642483a4a54a01d1578fe325802f88/}{permalink})
was automatically generated
from \href{https://github.com/habi/zmk-tooth-cohort-method-manuscript/tree/07a0a8aed6642483a4a54a01d1578fe325802f88}{habi/zmk-tooth-cohort-method-manuscript@07a0a8a}
on January 11, 2021.

@@

Micro-CT is a powerful tool to analyze and visualize the internal morphology of human permanent teeth.
It is increasingly used for investigation of epidemiological questions to provide the dentist with the necessary information required for successful endodontic treatment.
The aim of the present paper was to propose an image processing method to automate parts of the work needed to fully describe the internal morphology of human permanent teeth.

One hundred and four human teeth were scanned on a high-resolution micro-CT using an automatic specimen changer.
Python code in a Jupyter notebook was used to verify and process the scans, prepare the datasets for description of the internal morphology and to measure the apical region of he tooth.

The presented method offers an easy, non-destructive, rapid and efficient approach to scan, check and preview micro-computer tomographic datasets of a large number of teeth.
It is a helpful tool for the detailed description and characterization of the internal morphology of human permanent teeth using automated segmentation by means of micro-CT with full reproducibility and high standardization.

@@

\leavevmode\hypertarget{ref-10OKzEtEb}{}%
37. CC 810.30 Federal Act of 30 September 2011 on Research involving Human Beings (Human Research Act, HRA). \url{https://www.admin.ch/opc/en/classified-compilation/20061313/index.html}. Accessed 11 Jan 2021.
\end{cslreferences}

>>>>

A preprint of this manuscript is available on \emph{bioRxiv} at \url{https://doi.org/10.1101/2020.10.27.356998} and has been submitted to \href{https://bmcoralhealth.biomedcentral.com/}{\emph{BMC Oral Health}}.
This version of the manuscript \href{https://github.com/habi/zmk-tooth-cohort-method-manuscript/compare/f9b3333c625228f4f28211a34f381b9f87c430b0...b07ffd6d4f153f209ba316c2199aaa3684329b61}{has been updated} since the preprint deposition.

This manuscript
(\href{https://habi.github.io/zmk-tooth-cohort-method-manuscript/v/b07ffd6d4f153f209ba316c2199aaa3684329b61/}{permalink})
was automatically generated
from \href{https://github.com/habi/zmk-tooth-cohort-method-manuscript/tree/b07ffd6d4f153f209ba316c2199aaa3684329b61}{habi/zmk-tooth-cohort-method-manuscript@b07ffd6}
on February 22, 2021.

@@

High-resolution micro-computed tomography is a powerful tool to analyze and visualize the internal morphology of human permanent teeth.
It is increasingly used for investigation of epidemiological questions to provide the dentist with the necessary information required for successful endodontic treatment.
The aim of the present paper was to propose an image processing method to automate parts of the work needed to fully describe the internal morphology of human permanent teeth.

One hundred and four human teeth were scanned on a high-resolution micro-CT scanner susing an automatic specimen changer.
Python code in a Jupyter notebook was used to verify and process the scans, prepare the datasets for description of the internal morphology and to measure the apical region of the tooth.

The presented method offers an easy, non-destructive, rapid and efficient approach to scan, check and preview tomographic datasets of a large number of teeth.
It is a helpful tool for the detailed description and characterization of the internal morphology of human permanent teeth using automated segmentation by means of micro-CT with full reproducibility and high standardization.

@@

\leavevmode\hypertarget{ref-10OKzEtEb}{}%
37. Fedlex. \url{https://www.fedlex.admin.ch/eli/cc/2013/617/en}. Accessed 22 Feb 2021.
\end{cslreferences}
